### 2024-06-23 Paper/MSEPM-Manuscript.tex
Manuscript Revision

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniform factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype 
resembling a cell type with a linear association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait resembling obesity with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H}$$

@@

\begin{center}
    \begin{figure}
    \includegraphics[scale=.2]{Figures/Figure2.png}
    \footnotesize
    \caption*{\small \textbf{Figure 2:} (A) The MAE of the factor predictions on the testing set as multiple factors are modeled simultaneously. (B) Prediction methylation 
MAE as factors are included in the MSEPM model. (C) Model coefficients for Age, Sex, Continuous Normal and Continuous Exponential factors for models 
trained $(n = 500)$ with all four simulated factors. (D). Simulated and predicted methylation values for all simulated testing sites across all training folds. }
    \end{figure}
\end{center}

@@

\begin{raggedleft}
\begin{figure}
\includegraphics[scale=.15]{Figures/Figure4.png}
\footnotesize
\caption*{\small \textbf{Figure 4:} MSEPM model trained with age, sex, CT-PC1 and CT-PC2 predictions within testing 
set for methylation associated factors (A) age, (B) sex, (C) CT-PC1 and (D) CT-PC2. (E) Observed and predicted
 methylation values for training set has high concordance $(R^2=0.833, MAE=0.035)$}
\end{figure}
\end{raggedleft}

>>>>

We simulated individuals whose methylation is determined by four factors and their associated epigenetic factors: 
a uniform factor approximating age with a non-linear association with methylation status 
$$q \sim\mathcal{U}(0,100), s_{Age}=q^{0.5}, \text{Figure 1A-B}$$ a binary trait resembling sex, linearly associated 
with methylation status $$q \sim B(1,.5), s_{Sex}=q, \text{Figure 1C-D}$$ a continuous normal (CN) phenotype a linear 
association with methylation status $$q \sim\mathcal{N}(1, 0.1), s_{CN}=q, 
\text{Figure 1E-F}$$ and a 
continuous exponentially (CE) distributed trait with a linear association with methylation status 
$$q \sim \frac{1}{20}e^{-x/20}, s_{CE}=q, \text{Figure 1G-H}$$

@@

\begin{center}
    \begin{figure}
    \includegraphics[scale=.2]{Figures/Figure2.png}
    \footnotesize
    \caption*{\small \textbf{Figure 2:} (A) The MAE of the factor predictions on the testing set as multiple factors are modeled simultaneously and 
    (B) predicted methylation MAE as factors are included in the MSEPM model where the centerline is the 50th quantile and the box 
    with greatest width contains 50\% of the underlying data with each smaller box containing 50\% of the remaining data 
    with 6 levels of box width. (C) Model coefficients for 
Age, Sex, Continuous Normal and Continuous Exponential factors for models trained $(n = 500)$ with all four simulated 
factors. (D). Simulated and predicted methylation values for all simulated testing sites across all training fold }
    \end{figure}
\end{center}

@@

\begin{raggedleft}
\begin{figure}
\includegraphics[scale=.15]{Figures/Figure4.png}
\footnotesize
\caption*{\small \textbf{Figure 4:} MSEPM model trained with age, sex, CT-PC1 and CT-PC2 predictions within testing 
set for epigenetic factors (A) age, (B) sex, (C) CT-PC1 and (D) CT-PC2. (E) Observed and predicted
 methylation values for training set has high concordance $(R^2=0.933, MAE=0.035)$}
\end{figure}
\end{raggedleft}
